%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Re-apply Resume (copy)
% - This file is a copy of `sachinbglkt.tex` with ID placeholders
% - Replace the values of `\CandidateID` and `\ResumeID` before compiling
% - Compile with `pdflatex sachinbglkt_reapply.tex`
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%\tPACKAGES AND OTHER DOCUMENT CONFIGURATIONS 
%----------------------------------------------------------------------------------------
\documentclass{resume} % Use the custom resume.cls style 

\usepackage[left=0.4 in,top=0.15 in,right=0.4 in,bottom=0.3in]{geometry} % Document margins
\usepackage{hyperref} % For clickable links

% --- ID placeholders ---
% Set your candidate / resume IDs here before re-applying
\newcommand{\CandidateID}{REPLACE_WITH_CANDIDATE_ID}
\newcommand{\ResumeID}{REPLACE_WITH_RESUME_ID}

\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}

\name{Sachin} % Your name 
\address{%
\\ +91 7348976969 
\\ \href{mailto:sachinbglkt@gmail.com}{sachinbglkt@gmail.com} 
\\ BANGALORE, IN
}

\begin{document}
% \begin{rSection}{Objective}
% Seeking a position that will enable me to use my programming skills.
% \end{rSection}


%----------------------------------------------------------------------------------------
%\tEDUCATION SECTION
%----------------------------------------------------------------------------------------
\vspace{-10pt}
\begin{rSection}{Education}
{ MTech in Computer Science and Engineering, \textbf{IIIT Bangalore} ,  3.30/4} \hfill {2019-2021}
\\
{ B.E in Computer Science and Engineering , \textbf{KLESCET, Belagavi}  8.36/10} \hfill {2015-2019}

\end{rSection} 
\vspace{-7pt}

% Small Identifiers section for re-application convenience
\vspace{-7pt}
\begin{rSection}{Identifiers}
{\bf Candidate ID:} \CandidateID \\
{\bf Resume ID:} \ResumeID
\end{rSection}
\vspace{-7pt}

\begin{rSection}{Skills} \itemsep -3pt  

\begin{tabular}{ @{} >{\bfseries}l @{@\hspace{1.5ex}} l }
Languages: & Java, C, Data Structures and Algorithms \\
Technologies: & Spring Boot, Apache Kafka, Apache Spark, REST APIs, Maven, Git, Docker, RocksDB, ReactJS \\
Databases: & Cassandra, Azure SQL, BigQuery, PostgreSQL, GCP MySQL \\
\end{tabular}

\end{rSection}  

\vspace{-5pt}
\begin{rSection}{Work Experience}


% \end{rSubsection}
\begin{rSubsection}{SDE - III (July 2023 - Present)}{\textbf{Walmart Global Tech}}{} 

\vspace{-3pt}
\item Designed and implemented a dynamic extended-attributes feature for the Parts Finder, reducing product returns and improving conversion rates for auto-parts purchases.
\item Contributed to the design and development of a \textbf{scalable data ingestion platform} processing millions of fitment records daily with high availability and performance.
\item Architected and implemented \textbf{Fitment Analytics} Platform by processing Walmart’s item and fitment data using Spark and BigQuery, enabling scalable, low-latency reporting for downstream teams.
\item Developed a content ranking system for fitment, prioritizing data ingestion based on the rank of different data sources. 
\item Developed the Electronic Service Manual, reducing oil change order \textbf{processing time by 5 minutes} and tire installation time by \textbf{10 minutes} at Walmart store.

\item \textbf{Technologies:} Java, Spring Boot, Spark, RocksDb, Kafka, Cassandra, Azure SQL, BigQuery, GCP MySQL

\end{rSubsection}
\vspace{-7pt}
\begin{rSubsection}{SDE - II (July 2021 - July 2023)}{\textbf{Walmart Global Tech}}{} 

\vspace{-3pt}

\item Designed and developed an Excel-based fitment ingestion system used by \textbf{9,000+ small sellers}, eliminating reliance on costly ACES XML and giving Walmart a strategic advantage over platforms like Amazon and eBay.
\item Contributed to the development of the \textbf{Parts Finder and Content Quality Dashboards}, implementing features that provide insights into fitment data ingestion and item quality, respectively.


\item \textbf{Technologies:} Java, React, Metabase, Looker Studio, PostgreSQL, Maven


\end{rSubsection}

\vspace{-7pt}
\begin{rSubsection}{SDE - Intern (Jan 2021 - Jun 2021)}{\textbf{Walmart Global Tech}}{} 

\vspace{-3pt}

% \item Designed and developed a MiniSql engine using Java.
\item Developed reusable component libraries for use across the Walmart catalog organization, enhancing consistency and efficiency.
\item Written E2E test scripts and resolved numerous bugs in the Mantis tool which is Walmart's item catalog dashboard, enhancing system stability and reliability.


\end{rSubsection}

\end{rSection}
\vspace{-10pt}
\begin{rSection}{PROJECTS}

\begin{rSubsection}{Student Collaboration Portal - IIITB (Feb. 2020)}
{IIIT Bangalore}{}{}  %June 2016 - November 2016

\vspace{-3pt}

\item Developed a portal providing essential information for IIITB students, including modules for Previous Year Question Papers, Interview Experiences, and a Mock Interview Scheduler.
\item Focused on front-end development, enhancing user interface and experience.

\end{rSubsection}

\vspace{-10pt}

\begin{rSubsection}{Autonomous Traffic Control System (Aug. 2018)}{KLESCET}{} %January 2016 - April 2016

\vspace{-7pt}

\item Developed a system to address issues in traditional traffic management by using image processing algorithms to generate lane reference images.
\item Successfully tested in a Belgaum City lane with approval from the Commissioner of Belgaum, achieving satisfactory results. Awarded \textbf{Runner-up at the K-tech Innovation} Hub Project Exhibition.
 
\end{rSubsection}  

\end{rSection}

\vspace{-10pt}

\begin{rSection}{Academic \& Work Achievements} \itemsep -1pt    
\setlength{\leftskip}{-1em}

. \textbf{Two-time Bravo Award} winner for exceptional performance and exceeding work expectations. \\
. Institute Academic Award for being \textbf{Topper} in second semester engineering (one out of 500). \\
. Awarded by Dr. Mukhyamantri Chandru (Govt. of Karnataka) for securing \textbf{Highest Marks in Centre} (SSC). \\
. \textbf{Top 1\%} scorer in GATE 2019 exam. \\
. Cleared online contest and selected for onsite round (Dec. 2018) in ACM-ICPC (IIIT Pune region). \\
. \textbf{First place} in competitions: Code-Zilla (Mar. 2017, JCE BGM), TechnoQuiz (Apr. 2017, Google-IO Extended), CodeWar (Mar. 2018, KLESCET BGM), and Intra-College Coding Competition (Feb. 2019).

\end{rSection}

\end{document}
