%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% Resume Version 3 (ATS-safe Reapply)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass{resume}

\usepackage[left=0.4 in,top=0.15 in,right=0.4 in,bottom=0.3in]{geometry}
\usepackage{hyperref}

\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}

\name{Sachin}
\address{%
\\ +91 7348976969
\\ \href{mailto:sachinbglkt@gmail.com}{sachinbglkt@gmail.com}
\\ Bangalore, India
}

\begin{document}

%----------------------------------------------------------------------------------------
% SKILLS (Moved UP for ATS)
%----------------------------------------------------------------------------------------
\vspace{-10pt}
\begin{rSection}{Skills}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{1.5ex}} l }
Programming: & Java, C, Data Structures, Algorithms \\
Backend: & Spring Boot, REST APIs, Kafka, Spark, Maven, Git, Docker, RocksDB \\
Datastores: & Cassandra, BigQuery, Azure SQL, PostgreSQL, MySQL (GCP) \\
Frontend: & ReactJS \\
\end{tabular}

\end{rSection}

\vspace{-6pt}

%----------------------------------------------------------------------------------------
% EXPERIENCE
%----------------------------------------------------------------------------------------
\begin{rSection}{Professional Experience}

\begin{rSubsection}{Software Engineer III}{Walmart Global Tech}{Jul 2023 -- Present}{}
\vspace{-3pt}

\item Implemented a configurable extended-attributes framework for Parts Finder, enabling richer product metadata and lowering auto-parts return rates.
\item Built a distributed ingestion pipeline handling \textbf{multi-million fitment records daily}, optimized for throughput, fault tolerance, and scalability.
\item Created a Spark-based analytics workflow over item and fitment datasets, powering near real-time reporting via BigQuery.
\item Introduced priority-based ingestion logic by ranking upstream data sources, improving freshness and reliability of fitment data.
\item Delivered store-facing service workflows that reduced oil service handling time by \textbf{~5 minutes} and tire installation turnaround by \textbf{~10 minutes}.

\item \textbf{Environment:} Java, Spring Boot, Kafka, Spark, RocksDB, Cassandra, BigQuery, Azure SQL

\end{rSubsection}

\vspace{-7pt}

\begin{rSubsection}{Software Engineer II}{Walmart Global Tech}{Jul 2021 -- Jul 2023}{}
\vspace{-3pt}

\item Engineered a spreadsheet-driven fitment upload solution adopted by \textbf{9,000+ independent sellers}, replacing dependence on ACES XML standards.
\item Enhanced internal dashboards for Parts Finder and catalog quality, enabling teams to monitor ingestion accuracy and item health metrics.
\item Partnered with product and data teams to roll out seller-facing features with measurable adoption.

\item \textbf{Environment:} Java, ReactJS, PostgreSQL, Metabase, Looker Studio

\end{rSubsection}

\vspace{-7pt}

\begin{rSubsection}{Software Engineer Intern}{Walmart Global Tech}{Jan 2021 -- Jun 2021}{}
\vspace{-3pt}

\item Built shared UI and backend components reused across multiple catalog services.
\item Authored end-to-end test suites and fixed production defects in Walmart’s internal catalog management tooling.

\end{rSubsection}

\end{rSection}

\vspace{-8pt}

%----------------------------------------------------------------------------------------
% EDUCATION (Moved DOWN intentionally)
%----------------------------------------------------------------------------------------
\begin{rSection}{Education}

{ M.Tech — Computer Science and Engineering, \textbf{IIIT Bangalore} } \hfill {2019 -- 2021}
\\ GPA: 3.30 / 4.0

\vspace{3pt}

{ B.E — Computer Science and Engineering, \textbf{KLESCET, Belagavi} } \hfill {2015 -- 2019}
\\ GPA: 8.36 / 10

\end{rSection}

\vspace{-8pt}

%----------------------------------------------------------------------------------------
% PROJECTS
%----------------------------------------------------------------------------------------
\begin{rSection}{Selected Projects}

\begin{rSubsection}{Student Collaboration Portal}{IIIT Bangalore}{Feb 2020}{}
\vspace{-3pt}

\item Designed a student-facing platform aggregating academic resources, interview experiences, and mock interview scheduling.
\item Focused on front-end implementation with emphasis on usability and navigation.

\end{rSubsection}

\vspace{-6pt}

\begin{rSubsection}{Autonomous Traffic Control System}{KLESCET}{Aug 2018}{}
\vspace{-3pt}

\item Implemented an image-processing based traffic optimization system using lane density estimation.
\item Pilot-tested on a live city road; awarded \textbf{Runner-up} at K-tech Innovation Hub Exhibition.

\end{rSubsection}

\end{rSection}

\vspace{-10pt}

%----------------------------------------------------------------------------------------
% ACHIEVEMENTS
%----------------------------------------------------------------------------------------
\begin{rSection}{Achievements}

. Two-time recipient of Walmart \textbf{Bravo Award} for high-impact contributions. \\
. Institute Rank 1 holder in 1st year engineering. \\
. State-level recognition for securing highest SSC marks at examination center. \\
. Placed in \textbf{top 1\%} nationwide in GATE 2019. \\
. Qualified for onsite round of ACM-ICPC (IIIT Pune region). \\
. Winner of multiple competitive programming events across inter-college platforms.

\end{rSection}

\end{document}
